% !TEX root = thesis.tex
\clearpage
\begin{flushright}
    \thispagestyle{empty}
    \vspace*{\fill}
    \emph{In memory of my father}
    \vspace*{\fill}
\end{flushright}
\clearpage

\section*{Acknowledgements} 

The work presented in this thesis has been carried out between 2014 and 2019 at the University of Jyväskylä, at the University of Helsinki and at CERN. I would like to open my thesis by acknowledging the help I have received from several directions which has made my graduation possible.
\\~\\
\noindent
First, I thank my supervisors Dong Jo Kim and Jan Rak. Dong Jo for his continued guidance and patience and Jan for giving me the opportunity to work in this field.
\\~\\
\noindent
Additionally from our research group I would like to highlight Sami Räsänen for his help in both practical and physics matters and providing feedback to my thesis. I would also like to thank all present and past members of the ALICE Jyväskylä group for providing a supportive working environment.
\\~\\
\noindent For helping me get acquainted with the ALICE EMCal trigger maintenance work I am grateful to Jussi Viinikainen and Martin Poghoysan.
\\~\\
\noindent I would also like to acknowledge the support to finalising my analysis from the Jet Physics Working Group, especially Leticia Cunqueiro Mendez, Tatsuya Chujo and Marco van Leeuwen.
\\~\\
\noindent
I would like to thank the personnel of the Helsinki Institute of Physics detector laboratory for a pleasant working environment during my time in Helsinki and especially Erik Brücken, Timo Hildén and Essi Kangasaho for guiding me through the GEM quality assurance responsibilities. 
\\~\\
\noindent
I am grateful to Stefan Bathe and Marcin Chrząszcz for reviewing my thesis and providing useful comments and Jamie Nagle for agreeing to be my opponent.
\\~\\
\noindent
A special thanks goes to my family for all the support I have received both before and during my academic career. Without my parents none of this would have been possible.
\\~\\
\noindent
Finally I would like to acknowledge the financial support I have received from the University of Jyväskylä and the Helsinki Institute of Physics.
\\~\\
Jyväskylä, June 2019\\
Tomas Snellman